% This file was created with JabRef 2.7b.
% Encoding: UTF-8

\bibliographystyle{babplain-uh}
\bibliography{Bibliography}

\begin{thebibliography}{99}

\bibitem{TB Cooper and JH Kingston}TB Cooper and JH Kingston, “The Complexity of Timetable Construction Problems,”
in the Practice and Theory of Automated Timetabling, ed. EK Burke and P Ross,
pp. 283-295, Springer-Verlag (Lecture Notes in Computer Science), 1996. Basser
Department of Computer Science, University of Sydney, Australia

\bibitem{Carter's summary} MW Carter*, G Laporte†, and JW Chinneck, “A General Examination Scheduling
System,” Interfaces, vol. 24, no. 3, pp. 109-120, The Institute of Management Sciences,
May-June 1994. *Department of Industrial Engineering, University of
Toronto, Ontario, Canada; Ecole des Hautes Etudes Commerciales de Montreal,
Quebec, Canada; and Department of Systems and Computer Engineering, Carleton
University, Ottawa, Ontario, Canada

\bibitem{Bloomfield and McSharry says} SD Bloomfield and MM McSharry, “Preferential Course Scheduling,” Interfaces, vol.9, no. 4, pp. 24-31, The Institute of Management Sciences, August 1979. School of Business, Oregon State University, Corvallis, USA

\bibitem{Romero} BP Romero, “Examination Scheduling in a Large Engineering School: A
Computer-Assisted Participative Procedure,” Interfaces, vol. 12, no. 2, pp. 17-23, The
Institute of Management Sciences, April 1982. Industrial Organization Department,
Industrial Engineering Technical School, Madrid, Spain

\bibitem{survey of University of Nottingham} EK Burke, DG Elliman, PH Ford, and RF Weare, “Exam Timetabling in British
Universities – A Survey,” in the Practice and Theory of Automated Timetabling, ed. EK
Burke and P Ross, pp. 76-90, Springer-Verlag (Lecture Notes in Computer Science),
1996. Department of Computer Science, University of Nottingham, UK

\bibitem{VA Bardadym} VA Bardadym, “Computer-Aided School and University Timetabling: The New
Wave,” in the Practice and Theory of Automated Timetabling, ed. EK Burke and P Ross,
pp. 22-45, Springer-Verlag (Lecture Notes in Computer Science), 1996. International
Soros Science Education Program, International Renaissance Foundation,
Kiev, Ukraine

\bibitem{MW Carter} MW Carter, “A Survey of Practical Applications of Examination Timetabling Algorithms,”
Operations Research, vol. 34, no. 2, pp. 193-201, Operations Research Society
of America, March-April 1986. University of Toronto, Ontario, Canada

\bibitem{MW Carter and G Laporte} MW Carter* and G Laporte†, “Recent Developments in Practical Examination Timetabling,”
in the Practice and Theory of Automated Timetabling, ed. EK Burke and P
Ross, pp. 3-21, Springer-Verlag (Lecture Notes in Computer Science), 1996.
*Department of Industrial Engineering, University of Toronto, Ontario, Canada;
and ††Ecole des Hautes Etudes Commerciales de Montreal, Quebec, Canada

\bibitem{JH Kingston} JH Kingston*, VA Bardadym, and MW Carter, “Bibliography on the Practice and
Theory of Automated Timetabling,” in ftp://ftp.cs.usyd.edu.au/jeff/-
timetabling/timetabling.bib.gz. *Basser Department of Computer Science,
University of Sydney, Australia

\bibitem{D Abramson and J Abela}D Abramson and J Abela, T Arani*, and V Lotfi†, “A Three Phased Approach to
Final Exam Scheduling,” IIE Transactions, vol. 21, no. 1, pp. 86-96, IIE, Australia,
March 1989. (technical report)

\bibitem{D Corne and P Ross and HL Fang}D Corne, P Ross, and HL Fang, “Fast Practical Evolutionary Timetabling,” LectureNotes in Computer Science, vol. 865 (Artificial Intelligence and Simulation of
Behaviour (AISB) Workshop on Evolutionary Computing, University of Leeds, UK,
11th-13th April 1994), pp. 251-263, Springer-Verlag, 1994. Department of Artificial
Intelligence, University of Edinburgh, UK

\bibitem{B Paechter* and A Cumming* and H Luchian}B Paechter*, A Cumming*, H Luchian†, and M Petriuc‡, “Two Solutions to the General Timetable Problem using Evolutionary Methods,” proceedings of the IEEE
Conference on Evolutionary Computation 1994. *Computer Studies Department,
Napier University, Edinburgh, Scotland, UK; †Faculty of Computer Science, Al I
Cuza University of Iasi, Romania; and ‡Technical University of Iasi, Romania

\bibitem{EK Burke and DG Elliman and RF Weare 1}EK Burke, DG Elliman, and RF Weare, “The Automation of the Timetabling Process in Higher Education,” Journal of Educational Technology Systems, vol. 23, no. 4,
pp. 257-266, Baywood Publishing Company, 1995. Department of Computer Science,
University of Nottingham, UK

\bibitem{EK Burke and DG Elliman and RF Weare 2}EK Burke, DG Elliman, and RF Weare, “A Hybrid Genetic Algorithm for Highly Constrained Timetabling Problems,” 6th International Conference on Genetic Algorithms
(ICGA’95, Pittsburgh, USA, 15th-19th July 1995), Morgan Kaufmann, San Francisco,
CA, USA. Department of Computer Science, University of Nottingham, UK

\bibitem{EK Burke and DG Elliman and RF Weare 3}EK Burke, DG Elliman, and RF Weare, “Specialised Recombinative Operators for Timetabling Problems,” proceedings of the AISB (Artificial Intelligence and Simulation
of Behaviour) Workshop on Evolutionary Computing (University of Sheffield, UK, 3rd-7th
April 1995), pp. 75-85, Springer-Verlag, 1995. Department of Computer Science,
University of Nottingham, UK

\bibitem{EK Burke and JP Newall and RF Weare}EK Burke, JP Newall, and RF Weare, “A Memetic Algorithm for University Exam
Timetabling,” in the Practice and Theory of Automated Timetabling, ed. EK Burke and
P Ross, pp. 241-250, Springer-Verlag (Lecture Notes in Computer Science), 1996.
Department of Computer Science, University of Nottingham, UK

\bibitem{B Paechter and A Cumming and MG Norman and H Luchian}B Paechter*, A Cumming*, MG Norman†, and H Luchian‡, “Extensions to a Memetic Timetabling System,” in the Practice and Theory of Automated Timetabling,
ed. EK Burke and P Ross, pp. 251-265, Springer-Verlag (Lecture Notes in Computer
Science), 1996. *Computer Studies Department, Napier University, Edinburgh,
Scotland, UK; †Makespan Ltd, Edinburgh, UK; and ‡Faculty of Computer Science,
Al I Cuza University of Iasi, Romania

\bibitem{J Thompson and KA Dowsland}J Thompson and KA Dowsland, “Variants of Simulated Annealing for the Examination
Timetabling Problem,” Annals of Operations Research, 1995. European Business
Management School, University of Wales at Swansea, UK

\bibitem{J Thompson and KA Dowsland 2}J Thompson and KA Dowsland, “General Cooling Schedules for a Simulated
Annealing based Timetabling System,” in the Practice and Theory of Automated Timetabling,
ed. EK Burke and P Ross, pp. 345-363, Springer-Verlag (Lecture Notes in Computer Science), 1996. European Business Management School, University of Wales at Swansea, UK

\bibitem{JP Boufflet and S Negre}JP Boufflet and S N\`egre, “Three Methods used to solve an Examination Timetable
Problem,” in the Practice and Theory of Automated Timetabling, ed. EK Burke and P
Ross, pp. 327-344, Springer-Verlag (Lecture Notes in Computer Science), 1996.
D\'epartement de G\'enie Informatique, Universit\'e de Technologie de Compi\`egne, France

\bibitem{A Hertz}A Hertz, “Tabu Search for Large-Scale Timetabling Problems,” European Journal of
Operations Research, no. 54, pp. 39-47, 1991. D\'epartement d\'Informatique et de
Recherche Op\'erationelle, Universit\'e de Montr\'eal, Canada

\bibitem{A Hertz 2}A Hertz, “Finding a Feasible Course Schedule using Tabu Search,” Discrete Applied
Mathematics, vol. 35, no. 3, pp. 255-270, Elsevier Science Publishers, 1992.
D\'epartement d\'Informatique et de Recherche Op\'erationelle, Universit\'e de
Montr\'eal, Canada

\bibitem{L Kang and GM White}L Kang and GM White, “A Logic Approach to the Resolution of Constraints in
Timetabling,” European Journal of Operational Research, vol. 61, pp. 306-317, Elsevier
Science Publishers, 1992. Computer Science Department, University of Ottowa,
Ontario, Canada

\bibitem{C Cheng and L Kang and N Leung and GM White}C Cheng, L Kang, N Leung, and GM White, “Investigations of a Constraint Logic Programming Approach to University Timetabling,” in the Practice and Theory of
Automated Timetabling, ed. EK Burke and P Ross, pp. 112-129, Springer-Verlag (Lecture
Notes in Computer Science), 1996. Computer Science Department, University
of Ottawa, Canada

\bibitem{P Boizumault and Y Delon and L Peridy}P Boizumault, Y Delon, and L P\'eridy*, ``A CLP Approach for Examination Planning,''Constraint Processing: Selected Papers, Lecture Notes in Artificial Intelligence,
Springer-Verlag, 1995. *Institut de Math\'ematiques Appliqu\'ees, Universit\'e Catholique
de l\'Ouest, Angers, France

\bibitem{P Boizumault and C Gueret and N Jussien}P Boizumault*, C Gu\'eret†, and N Jussien, “Efficient Labelling and Constraint Relaxation for Solving Timetabling Problems,” Proceedings of the Workshop on Constraint
Languages and their use in Problem Modelling, International Logic Programming Symposium
(Ithaca, New York, USA, 18th Nov 1994), pp. 116-130. *Ecole des Mines de
Nantes, France; and †Institut de Math\'ematiques Appliqu\'ees, Universit\'e Catholique
de l\'Ouest, Angers, France

\bibitem{C Gueret and N Jussien and P Boizumault and C Prins}C Gu\'eret*, N Jussien†, P Boizumault†, and C Prins†, “Building University Timetables Using Constraint Logic Programming,” in the Practice and Theory of Automated
Timetabling, ed. EK Burke and P Ross, pp. 130-145, Springer-Verlag (Lecture Notes
in Computer Science), 1996. *Institut de Math\'ematiques Appliqu\'ees, Universit\'e
Catholique de l\'Ouest, Angers, France; and †Ecole des Mines de Nantes, France

\bibitem{Carla P. Gomes}Carla P. Gomes, Henry Kautz, Ashish Sabharwal, Bart Selman (2008). "Satisfiability Solvers". In Frank Van Harmelen, Vladimir Lifschitz, Bruce Porter. Handbook of knowledge representation. Foundations of Artificial Intelligence. 3. Elsevier. pp. 89–134.

\end{thebibliography}